An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-10-06 poly-embed-journal/poly-embed-journal.tex
Fix typo in proof of theorem 9

	It is just left to show (ii).
	Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that $H_{(w,b)}$ uniquely determines a facet of $P$.
	The result then follows if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
	As halfspaces are uniquely determined, this is only true if some $H_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
	\jessiet{This is super hand-wavy, and not nearly as precise as I'd like, but it's a first pass.}
  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}

>>>>

	It is just left to show (ii).
	Suppose for contradiction that there was a set of closed halfspaces $\H$ such that $P = \cap \H$, but there was a $H^+_{(w,b)} \in \H^* \setminus \H$, and therefore $\H^* \not \subseteq \H$.
	By (i), we know that $H_{(w,b)}$ uniquely determines a facet of $P$.
	A contradiction then emerges if there is no set of $\H' := \{H^+_{(w_i, b_i)}\}_{i=1}^l \subseteq \H \setminus \H^*$ such that $\cap \H' = H_{(w,b)}$.
	As halfspaces are uniquely determined, this is only true if some $H^+_{(w_i,b_i)} \in \H'$ is precisely equal to $H^+_{(w,b)}$, contradicting the assumption that $\H^* \not \subseteq \H$.
	\jessiet{This is super hand-wavy, and not nearly as precise as I'd like, but it's a first pass.}
  \jessiet{\url{https://arxiv.org/abs/0805.0292} Prop 4.5? Ziegler Lectures on Polytopes Theorem 2.15 (7) also kind of close to this, but on polytopes not polyhedron.}
\end{proof}
